---
title: "Stat 128 Term Project R Notebook"
output: html_notebook
author: 'Dean Chiang'
---

# Question D.

- According to [UWM Busar's Office](http://www.bussvc.wisc.edu/bursar/termcode.html), academic year 2017 has the term codes 1174, 1176, 1182

```{r}
date()
```

## Import Data: instructors.id, name, 18737 rows

```{r}
library(readr)
instructors <- read_csv("C:/Users/dchiang/Downloads/uwm/instructors.csv")
View(instructors)
summary(instructors)
```

## Import Data: teachings.instructor_id, section_uuid, 315211 rows

```{r}
library(readr)
teachings <- read_csv("C:/Users/dchiang/Downloads/uwm/teachings.csv")
View(teachings)
```

## Import Data: sections.uuid, course_offering_uuid, 315602 rows

```{r}
library(readr)
sections <- read_csv("C:/Users/dchiang/Downloads/uwm/sections.csv")
View(sections)
```

## Import Data: grade_distributions.course_offering_uuid, grade_counts, 193262 rows

```{r}
library(readr)
grades <- read_csv("C:/Users/dchiang/Downloads/uwm/grade_distributions.csv")
View(grades)
```

## Calcuate GPA per course offering

```{r}
# total body count
grades$sumcount <- grades$a_count + grades$ab_count + grades$b_count + grades$bc_count + grades$c_count + grades$d_count + grades$f_count + grades$s_count + grades$u_count + grades$cr_count + grades$n_count + grades$p_count + grades$i_count + grades$nw_count + grades$nr_count + grades$other_count
summary(grades$sumcount)
# Grade points total
grades$gpsum <- grades$a_count*4 + grades$ab_count*3.5 + grades$b_count*3 + grades$bc_count*2.5 + grades$c_count*2 + grades$d_count*1 + grades$f_count*0 + grades$s_count*2 + grades$u_count*0 + grades$cr_count*2 + grades$n_count*0 + grades$p_count*2 # + grades$i_count + grades$nw_count + grades$nr_count + grades$other_count REST DONT COUNT
summary(grades$gpsum)
# GPA per row
grades$gpa <- grades$gpsum / grades$sumcount
summary(grades$gpa)
```

## Import Data: course_offerings.uuid, term_code, 81452 rows

```{r}
library(readr)
course_offerings <- read_csv("C:/Users/dchiang/Downloads/uwm/course_offerings.csv")
View(course_offerings)
```

## Merge Relevant data frames to get Instructor, Grades, and Terms together

```{r}
df1 <- merge(instructors, teachings, by.x = 'id', by.y = 'instructor_id')
summary(df1)
```
```{r}
df2 <- merge(df1, sections, by.x = 'section_uuid', by.y = 'uuid')
summary(df2)
df3 <- df2[c('section_uuid', 'id', 'name', 'course_offering_uuid')]
summary(df3)
```
- [Delete columns](https://stackoverflow.com/questions/4605206/drop-data-frame-columns-by-name)
- [Rename Columns](http://rprogramming.net/rename-columns-in-r/)

```{r}
df4 <- merge(df3, course_offerings, by.x = 'course_offering_uuid', by.y = 'uuid')
summary(df4)
names(df4) <- c('course_offering_uuid', 'section_uuid', 'teacher_id', 'teacher_name', 'course_uuid', 'term_code', 'course_name')
head(df4, 5)
```

## Merge the instructor and term info into one big grades table 2076665 rows

```{r}
gpat <- grades[c('course_offering_uuid', 'gpa')]
# head(gpat, 5)
gpatt <- merge(gpat, df4, by.x = 'course_offering_uuid', by.y = 'course_offering_uuid')
summary(gpatt)
```

### Does it matter merging tables one before another? No

```{r}
df5 <- merge(df4, gpat, by.x = 'course_offering_uuid', by.y = 'course_offering_uuid')
summary(df5)
```

## Average GPA per Instructor per Term

- [Export data](https://www.statmethods.net/input/exportingdata.html)

```{r}
write.csv(df5, 'C:\Users\dchiang\Downloads\data\gpa_instr_term.csv')
```

- [SQL Group by](https://stackoverflow.com/questions/27193373/what-is-the-r-equivalent-of-sql-select-from-table-group-by-c1-c2)

```{r}
# install.package('sqldf', dependencies = T)
library(sqldf)
df6 <- sqldf('SELECT * FROM df5 GROUP BY teacher_id, term_code')
summary(df6)
# Alternative: aggregate()
# aggregate(df,by=list(df$c3,df$c4),FUN=head,1)
```

```{r}
library(plyr)
termcnt <- count(df6, vars = c('term_code'))
nrow(insterm)
instrcnt <- count(df6, 'teacher_id')
nrow(instrcnt)
termcodes <- count(course_offerings, 'term_code')
nrow(termcodes) # only 22 unique terms
```

## Plot Average GPA per Term per Instructor

```{r}
library(ggplot2)
```

- [Subsetting](https://www.statmethods.net/management/subset.html)

```{r}
sub1 <- subset(df6, df6$teacher_id < 3056695)
# FAIL--[which(df6$teacher_id < 3056695)]
#gplot <- ggplot(data = df6, aes(x=teacher_id, y=term_code, color=gpa))
gplot <- ggplot(data = sub1, aes(x=teacher_id, y=term_code, color=gpa))
gplot+geom_point()
```

*CANNOT visually detect any pattern or trend.*

# Question E.

1. According to [UWM Busar's Office](http://www.bussvc.wisc.edu/bursar/termcode.html), academic year 2017 has the term codes 1174, 1176, 1182
2. Extract 2017 records
3. Count frequency of teachers per course 
4. [Sort data](https://www.statmethods.net/management/sorting.html)
5. [Sort function](https://stackoverflow.com/questions/19727029/how-do-i-get-a-list-sorted-by-frequency-in-r)

```{r}
gpa2017 <- subset(df6, df6$term_code == c(1174,1176,1182))
summary(gpa2017)
# year2017 has 316 rows
```
```{r}
fav2017cnt <- count(gpa2017, vars = c('course_name')) # , 'teacher_name'
summary(fav2017cnt)
# reduced 3129 rows to 1455 rows with max=182
fav2017o <- fav2017cnt[order(fav2017cnt$freq, decreasing = T),]
head(fav2017o, 10)
```

#### PIck a subject to find instructors

```{r}
favs1 <- subset(gpa2017, gpa2017$course_name == 'General Physics')
summary(favs1)
instrs1 <- favs1$teacher_name
instrs1
```

### Find professors ratings at [ratemyprofessor](https://www.ratemyprofessors.com/campusRatings.jsp?sid=1256)

#### Issues

1. [Professor Personal Page] contains
```{html}
ShowRatings.jsp?tid=994788
<div class="rating-breakdown">
        <div class="left-breakdown">
          <span class="take-again-help-text help-text"> Percentage excludes ratings added prior to 05/25/16. </span>
          <div class="breakdown-wrapper">
            <div class="breakdown-header quality-header">
              <div class="breakdown-container quality">
                <div>
                  Overall Quality
                  <div class="grade" title="">2.0</div>
```
2. [Initial School Page]
(https://www.ratemyprofessors.com/campusRatings.jsp?sid=1256)
only shows a few professors.
3. Even after clicking on the Show All Professor button 
to see [this page]
(https://www.ratemyprofessors.com/search.jsp?queryBy=schoolId&schoolName=University+of+Wisconsin+-+Madison&schoolID=1256&queryoption=TEACHER)
only a limited number of the professors are returned on 
a dynamically generated side bar which does not show all 
professors still (4433 professors found)
4. But most challenging task is that the professor names 
in the overall rating list are shown last name first 
and in proper case, while the instructor name in our data 
consist of full (first then last) name in all all upper case.

#### Professor Matt Herndon of Physics Dept (rating: 2.0)

```{r}
gpa.matt <- subset(df6, df6$teacher_name == 'MATTHEW HERNDON' & df6$course_name == 'General Physics')
summary(gpa.matt)
View(gpa.matt)
# Visual inspection shows a increasing avg GPA
```

_END OF FILE_