---
title: "Stat 128 Sprint 2019 Term Project R Notebook"
output: html_notebook
author: 'Dean Chiang'
---

```{r}
date()
```
# UWM Metadata

## 1. Download Data

1. Download data from
[UW Madison Courses and Grades 2006-2017](https://www.kaggle.com/Madgrades/uw-madison-courses)
(login required)
2. Local database: [sqlite](/Users/dean/Downloads/data/uwm/database.sqlite3)
3. Local data files: [csv](/Users/dean/Downloads/data/uw-madison-courses)

## 2. Load Data

```{r}
require(RSQLite)
dbpath <- '/Users/dchiang/Downloads/data/uwm/database.sqlite3'
dbpath <- '~/Downloads/data/uwm/database.sqlite3'
myconn = dbConnect(drv=SQLite(), dbname=dbpath)
str(myconn)
```

### List of Tables in database

```{r}
tbls <- dbListTables(myconn)
# class(tbls) # 'character'
for (t in tbls) { print(t) }
```

### List of Fields per Table

```{r}
# dbListFields(myconn, 'course_offerings')
i <- 0
for (t in tbls) {
  i <- i + 1
  print('========')
  print(tbls[i])
  print('----------------')
  fields <- dbListFields(myconn, tbls[i])
  print(fields)
}
```

## Join Sections to Teachers
```{r}
sqlwhere <- 'SELECT * FROM sections \
INNER JOIN teachings \
ON sections.uuid=teachings.section_uuid'
section.teachers <- dbGetQuery(myconn, sqlwhere)
str(section.teachers)
```

- [R function count()](https://www.rdocumentation.org/packages/plyr/versions/1.8.4/topics/count)
- [R library plyr](https://www.rdocumentation.org/packages/plyr/versions/1.8.4)

```{r}
library(plyr)
section.teachers$instructor_id <- factor(section.teachers$instructor_id)
sections.per.teacher <- count(section.teachers, 'instructor_id')
str(sections.per.teacher)
```

### Histogram of Sections Frequency Per Teacher
```{r}
hist(sections.per.teacher$freq)

```

## Sections Per Term

### Join Course Offerings into Sections to Append Terms
```{r}
sqlwhere2 <- 'SELECT * FROM sections \
INNER JOIN course_offerings \
ON sections.course_offering_uuid=course_offerings.uuid'
section.courses <- dbGetQuery(myconn, sqlwhere2)
str(section.courses)
```

```{r}
head(section.courses, 3)
```

### Calculate Sections per Term
```{r}
sections.per.term <- count(section.courses, 'term_code')# vars = c('uuid', 'term_code'))
str(sections.per.term)
```
```{r}
#hist(sections.per.term$freq)
plot(sections.per.term$term_code, sections.per.term$freq)
```

## Determine number of courses over entire time period taught in each subject code

### Join Section and Grades
```{r}
sqlwhere3 <- 'SELECT * FROM grade_distributions \
INNER JOIN subject_memberships \
ON grade_distributions.course_offering_uuid=subject_memberships.course_offering_uuid'
grade.subject <- dbGetQuery(myconn, sqlwhere3)
str(grade.subject)
```

### Count Frequency of Courses per Subject code
```{r}
course.per.subject <- count(grade.subject, 'subject_code')
str(course.per.subject)
#View(course.per.subject)
```

```{r}
hist(course.per.subject$freq)
```

```{r}
plot(course.per.subject$subject_code, course.per.subject$freq)
```

```{r}
require(ggplot2)

```
```{r}
p1 <- ggplot(data = course.per.subject, aes(x = course.per.subject$freq))
p1+geom_histogram(fill='gray', color = 'white')+theme_minimal()
```
```{r}
p2 <- ggplot(data = grade.subject, aes(x = grade.subject$subject_code))
#factor(grade.subject$subject_code), y=count(grade.subject$course_offering_uuid)$freq
p2+geom_histogram(fill = 'gray', color = 'white')+theme_minimal()
```

## Calculate the Average of the Course Grade per Section

```{r}
dbReadTable(myconn, 'grade_distributions')
```

