---
title: "Stat 128 Term Project R Notebook"
output: html_notebook
author: 'Dean Chiang'
---

# Question C

```{r}
date()
```

## Import Data: instructors.id, name, 18737 rows

```{r}
library(readr)
instructors <- read_csv("C:/Users/dchiang/Downloads/uwm/instructors.csv")
View(instructors)
summary(instructors)
```

## Import Data: teachings.instructor_id, section_uuid, 315211 rows

```{r}
library(readr)
teachings <- read_csv("C:/Users/dchiang/Downloads/uwm/teachings.csv")
View(teachings)
```

## Import Data: sections.uuid, course_offering_uuid, 315602 rows

```{r}
library(readr)
sections <- read_csv("C:/Users/dchiang/Downloads/uwm/sections.csv")
View(sections)
```

## Import Data: grade_distributions.course_offering_uuid, grade_counts, 193262 rows

```{r}
library(readr)
grades <- read_csv("C:/Users/dchiang/Downloads/uwm/grade_distributions.csv")
View(grades)
```

## Calcuate GPA per course offering

```{r}
# total body count
grades$sumcount <- grades$a_count + grades$ab_count + grades$b_count + grades$bc_count + grades$c_count + grades$d_count + grades$f_count + grades$s_count + grades$u_count + grades$cr_count + grades$n_count + grades$p_count + grades$i_count + grades$nw_count + grades$nr_count + grades$other_count
summary(grades$sumcount)
# Grade points total
grades$gpsum <- grades$a_count*4 + grades$ab_count*3.5 + grades$b_count*3 + grades$bc_count*2.5 + grades$c_count*2 + grades$d_count*1 + grades$f_count*0 + grades$s_count*2 + grades$u_count*0 + grades$cr_count*2 + grades$n_count*0 + grades$p_count*2 # + grades$i_count + grades$nw_count + grades$nr_count + grades$other_count REST DONT COUNT
summary(grades$gpsum)
# GPA per row
grades$gpa <- grades$gpsum / grades$sumcount
summary(grades$gpa)
```

## Import Data: course_offerings.uuid, term_code, 81452 rows

```{r}
library(readr)
course_offerings <- read_csv("C:/Users/dchiang/Downloads/uwm/course_offerings.csv")
View(course_offerings)
```

## Merge Relevant data frames to get Instructor, Grades, and Terms together

```{r}
df1 <- merge(instructors, teachings, by.x = 'id', by.y = 'instructor_id')
summary(df1)
```
```{r}
df2 <- merge(df1, sections, by.x = 'section_uuid', by.y = 'uuid')
summary(df2)
df3 <- df2[c('section_uuid', 'id', 'name', 'course_offering_uuid')]
summary(df3)
```
- [Delete columns](https://stackoverflow.com/questions/4605206/drop-data-frame-columns-by-name)
- [Rename Columns](http://rprogramming.net/rename-columns-in-r/)

```{r}
df4 <- merge(df3, course_offerings, by.x = 'course_offering_uuid', by.y = 'uuid')
summary(df4)
names(df4) <- c('course_offering_uuid', 'section_uuid', 'teacher_id', 'teacher_name', 'course_uuid', 'term_code', 'course_name')
head(df4, 5)
```

## Merge the instructor and term info into one big grades table 2076665 rows

```{r}
gpat <- grades[c('course_offering_uuid', 'gpa')]
# head(gpat, 5)
gpatt <- merge(gpat, df4, by.x = 'course_offering_uuid', by.y = 'course_offering_uuid')
summary(gpatt)
```

### Does it matter merging tables one before another? No

```{r}
df5 <- merge(df4, gpat, by.x = 'course_offering_uuid', by.y = 'course_offering_uuid')
summary(df5)
```

## Average GPA per Instructor per Term

- [Export data](https://www.statmethods.net/input/exportingdata.html)

```{r}
write.csv(df5, 'C:\Users\dchiang\Downloads\data\gpa_instr_term.csv')
```

- [SQL Group by](https://stackoverflow.com/questions/27193373/what-is-the-r-equivalent-of-sql-select-from-table-group-by-c1-c2)

```{r}
# install.package('sqldf', dependencies = T)
library(sqldf)
df6 <- sqldf('SELECT * FROM df5 GROUP BY teacher_id, term_code')
summary(df6)
# Alternative: aggregate()
# aggregate(df,by=list(df$c3,df$c4),FUN=head,1)
```

```{r}
library(plyr)
termcnt <- count(df6, vars = c('term_code'))
nrow(insterm)
instrcnt <- count(df6, 'teacher_id')
nrow(instrcnt)
termcodes <- count(course_offerings, 'term_code')
nrow(termcodes) # only 22 unique terms
```

## Plot Average GPA per Term per Instructor

```{r}
library(ggplot2)
```

```{r}
sub1 <- subset(df6, df6$teacher_id < 3056695)
# FAIL--[which(df6$teacher_id < 3056695)]
#gplot <- ggplot(data = df6, aes(x=teacher_id, y=term_code, color=gpa))
gplot <- ggplot(data = sub1, aes(x=teacher_id, y=term_code, color=gpa))
gplot+geom_point()
```

*CANNOT visually detect any pattern or trend.*

//