---
title: "Stat 128 Project R Notebook"
author: 'Dean Chiang'
date: "April 22, 2019"
output: html_notebook
---


# Stat 128 Spring 2019 Student Project - Fish Passage Assessment Database ds69

Data source

- [20 Most Recent Public BIOS Data Layers](https://www.wildlife.ca.gov/Data/BIOS/Latest-Datasets)
- [HTML metadata](https://map.dfg.ca.gov/metadata/ds0069.html) - but this download is for file geodatabase and LYR file only
- [CNRA open data page](https://data.cnra.ca.gov/organization/california-department-of-fish-and-wildlife/portal/data)
- [CDFW ArcGIS open data page](http://data-cdfw.opendata.arcgis.com/datasets/california-fish-passage-assessment-database-ds69-1) where the data can be downloaded as shapefile  (include dbf) or csv.
- [csv download link](http://data-cdfw.opendata.arcgis.com/datasets/1df90a95e4c348f1bd06326fd96ced78_0)
- [Open DataGeoService](https://tiles.arcgis.com/tiles/Uq9r85Potqm3MfRV/arcgis/rest/services/biosds69_cmu/MapServer/0/query?outFields=*&where=1%3D1)
- [Open Data GeoJSON](https://opendata.arcgis.com/datasets/b10f4d39932f4c18b619003038c6585a_0.geojson)
- [AGOL Feature Layer item](https://www.arcgis.com/home/item.html?id=1df90a95e4c348f1bd06326fd96ced78)
- [AGOL FeatureServer](https://services2.arcgis.com/Uq9r85Potqm3MfRV/arcgis/rest/services/biosds69_fmu/FeatureServer/0)
- [AGOL Tile Layer item](https://www.arcgis.com/home/item.html?id=b10f4d39932f4c18b619003038c6585a)
- [AGOL Cached MapServer](https://tiles.arcgis.com/tiles/Uq9r85Potqm3MfRV/arcgis/rest/services/biosds69_cmu/MapServer)
- [Geo service](https://services2.arcgis.com/Uq9r85Potqm3MfRV/arcgis/rest/services/biosds69_fmu/FeatureServer/0/query?outFields=*&where=1%3D1)
- [GeoJSON](https://opendata.arcgis.com/datasets/1df90a95e4c348f1bd06326fd96ced78_0.geojson)
- Data downloaded as [csv](C:/Users/dchiang/Downloads/California_Fish_Passage_Assessment_Database_ds69.csv) and [shapefile](~/Downloads/California_Fish_Passage_Assessment_Database_ds69.zip)


## Download and Import Data File
```{r}
library(readr)
# biosds69 <- read_csv("C:/Users/dchiang/Downloads/biosds69.csv")
# View(biosds69)
```

## Load the Data directly from the Internet
```{r}
biosds69 <- read.csv('https://opendata.arcgis.com/datasets/1df90a95e4c348f1bd06326fd96ced78_0.csv')
View(biosds69)
dim(biosds69)
```

## Check data
```{r}
class(biosds69)
str(biosds69)
```

### Data Summary
```{r}
summary(biosds69)
```


