---
title: "Stat 128 Project Metadata R Notebook"
output: html_notebook
author: 'Dean Chiang'
---

```{r}
date()
```

## 1. Download Data

1. Download data from
[UW Madison Courses and Grades 2006-2017](https://www.kaggle.com/Madgrades/uw-madison-courses)
(login required)
2. Local database: [sqlite](/Users/dean/Downloads/data/uwm/database.sqlite3)
3. Local data files: [csv](/Users/dean/Downloads/data/uw-madison-courses)

## 2. Load Data

```{r}
require(RSQLite)
myconn = dbConnect(drv=SQLite(), dbname='/Users/dean/Downloads/data/uwm/database.sqlite3')
str(myconn)
```

### List of Tables and Fields
```{r}
tbls <- dbListTables(myconn)
# class(tbls) # 'character'
for (t in tbls) { print(t) }
```
```{r}
# dbListFields(myconn, 'course_offerings')
i <- 0
for (t in tbls) {
  i <- i + 1
  print('========')
  print(tbls[i])
  print('----------------')
  fields <- dbListFields(myconn, tbls[i])
  print(fields)
}
```

## Join Sections to Teachers
```{r}
sqlwhere <- 'SELECT * FROM sections \
INNER JOIN teachings \
ON sections.uuid=teachings.section_uuid'
section.teachers <- dbGetQuery(myconn, sqlwhere)
str(section.teachers)
```

[R function count()](https://www.rdocumentation.org/packages/plyr/versions/1.8.4/topics/count)

```{r}
library(plyr)
sections.per.teacher <- count(section_teachers, 'instructor_id')
str(sections.per.teacher)
```
```{r}
hist(sections.per.teacher$freq)

```

## Sections Per Term
### Join Course Offerings into Sections to Append Terms
```{r}
sqlwhere2 <- 'SELECT * FROM sections INNER JOIN course_offerings \
ON sections.course_offering_uuid=course_offerings.uuid'
section.courses <- dbGetQuery(myconn, sqlwhere2)
str(section.courses)
```

### Calculate Sections per Term
```{r}
sections.per.term <- count(section.courses, 'term_code')# vars = c('uuid', 'term_code'))
str(sections.per.term)
```
```{r}
#hist(sections.per.term$freq)
plot(sections.per.term$term_code, sections.per.term$freq)
```

## Determine number of courses over entire time period taught in each subject code

### Join Section and Grades
```{r}
sqlwhere3 <- 'SELECT * FROM grade_distributions INNER JOIN subject_memberships \
ON grade_distributions.course_offering_uuid=subject_memberships.course_offering_uuid'
grade.subject <- dbGetQuery(myconn, sqlwhere3)
str(grade.subject)
```

### Count Frequency of Courses per Subject code
```{r}
course.per.subject <- count(grade.subject, 'subject_code')
str(course.per.subject)
```

