---
title: "Stat 128 EXam 3 (Final) R Notebook"
output: html_notebook
author: "Dean Chiang"
---
```{r}
date()
```

## 1. Normal distribution of hit songs is 220 s with stdev of 60 s
```{r}

```

### 1.a. Percentage of hit songs over 5 minutes
```{r}
pct5 <- pnorm(300, mean = 220, sd=60)
pct5

```


### 1.b. Percent hit songs between 3 and 4 min
```{r}
pct3m <- pnorm(180, mean = 220, sd = 60)
pct4m <- pnorm(240, mean = 220, sd = 60)
pct4m - pct3m
```

### 1.c. 25th Percentile of of length of hit songs
```{r}
pct25 <- qnorm(0.25, mean = 220, sd = 60)
pct25
```

### 1.d. Heigth of the normal curve at x=200
```{r}
ht <- dnorm(200, mean = 220, sd = 60)
ht
```

### 1.e. Randomly generate 10 hit song lengths
```{r}
hits <- rnorm(10, mean = 220, sd = 60)
hits
```


## 2. Matrix calculation
```{r}
X <- matrix(c(7, 1, -6, 5, 2, 8, 3, 9, 10), ncol = 3, nrow = 3)
X
```

### 2.a. Multiply each element of X by 5
```{r}
Y <- X * 5
Y
```

### 2.c. Transpose of X multiplied by X
```{r}
Xt <- t(X)
Xt
XtX <- Xt %*% X
XtX
```

### 2.d. Verify Inverse of X multiplied by X is the Identity matrix
```{r}
invx <- solve(X)
idmat <- invx %*% X
round(idmat)
```

## 3. 
```{r}
library(MASS)
head(UScereal, 3)
```

### 3.a. Construct scatter plot displaying calories on x-axis and fiber on y-axis. Color code the dots to represent manufacturer.
```{r}

```

### 3.b. Same as part (a) except facet on manufacturer
```{r}

```


## 4. Exercise in SQLite
```{r}
str(state.x77)
state_x77_new <- data.frame(state.x77)
state_x77_new$state = row.names(state_x77_new)
row.names(state_x77_new) <- NULL
head(state_x77_new, 2)
```

```{r}
state_region_new <- data.frame(state.region)
state_region_new$state <- state_x77_new$state
head(state_region_new, 3)
```

### 4.a. Set db connection
```{r}
library(RSQLite)

```

#### Create local database
```{r}
examconn = dbConnect(RSQLite::SQLite(), '/Users/dchiang/Downloads/data/state_db.sqlite')
```
#### Create tables
```{r}
dbWriteTable(examconn, 'state_x77_new', value = state_x77_new)
dbWriteTable(examconn, 'state_region_new', value = state_region_new)

```

### 4.b. List tables
```{r}
tablelist <- dbListTables(examconn)
tablelist
```

### 4.c. List fiels in state_x77_new table
```{r}
x77fields <- dbListFields(examconn, 'state_x77_new')
x77fields
```

### 4.d. Select only Frost and Income fields from table
```{r}
sqlwhere1 <- 'SELECT Frost, Income FROM state_x77_new'
frost.income <- dbGetQuery(examconn, sqlwhere1)
head(frost.income, 3)
```

### 4.e. Join the 2 tables in state
```{r}
sqlwhere42 <- 'SELECT * FROM state_x77_new \
INNER JOIN state_region_new \
ON state_x77_new.state=state_region_new.state'
state_x77_region <- dbGetQuery(examconn, sqlwhere42)
## str(state_x77_region)
head(state_x77_region, 3)
```

### 4. f. Counf of state per region in new joined table
```{r}
state_x77_region$state <- factor(state_x77_region$state)
state_x77_region$region <- factor(state_x77_region$state.region)
states.per.region <- count(state_x77_region, 'state.region')
str(states.per.region)
head(states.per.region, 5)
```

## 5. Regression (Extra Credit)

### 5.a. Using the UScereal data in MASS package, build a multiple linear regression model to predict _sugars_ based on protein, fat, carbo, and calories. What is the coefficient of determination?
```{r}
library(MASS)
summary(UScereal)
sugarsm <- lm(sugars~protein+fat+carbo+calories, data = UScereal)
summary(sugarsm)
```
r2 = 0.8941

### 5.b. Use the model to predict the sugars for a cereal with protein = 5, fat = 1, carbo = 20, and calories = 150.
```{r}

```



### 5.c. Give the coefficient of protein and interpretation in this context.

