---
title: "Stat 128 Spring 2019 Term Project R Notebook"
output: html_notebook
author: "Kristin Van Gaasbeck"
---


# Stat 128 Term Project

**Data Source**

- Download from [UW Madison Courses and Grades 2006-2017](https://www.kaggle.com/Madgrades/uw-madison-courses)
(login required)
2. Local database: [sqlite: Mac OSX path](/Users/kvan/Downloads/data/uwm/database.sqlite3)
3. Local data files: [csv: Windows path](C:\Users\kvan\Downloads\data\uw-madison-courses)

-------------------------------------------------------- 

#Script to load the raw data - we may not need all of these files later on
#Imported from my desktop, after downloading from Kaggle.com

```{r}
course_offerings <- read.csv("~/Downloads/data/uwm/course_offerings.csv")
courses <- read.csv("~/Downloads/data/uwm/courses.csv")
grade_distributions <- read.csv("~/Downloads/data/uwm/grade_distributions.csv")
instructors <- read.csv("~/Downloads/data/uwm/instructors.csv")
rooms <- read.csv("~/Downloads/data/uwm/rooms.csv")
schedules <- read.csv("~/Downloads/data/uwm/schedules.csv")
sections <- read.csv("~/Downloads/data/uwm/sections.csv")
subject_memberships <- read.csv("~/Downloads/data/uwm/subject_memberships.csv")
subjects <- read.csv("~/Downloads/data/uwm/subjects.csv")
teachings <- read.csv("~/Downloads/data/uwm/teachings.csv")

```

#Question a) Compute average GPA of each section

```{r}
grades.sections <- merge(grade_distributions,sections,by.x=c('course_offering_uuid', 'section_number'), by.y=c('course_offering_uuid','number'))
summary(grades.sections)
```

#There are duplicates when matching the course_offering_uuid and section_number.

```{r}
library(plyr)  #useful for organizing and breaking down data for analysis
freq.of.course.and.section = count(grades.sections, vars=c('course_offering_uuid', 'section_number'))
sum(freq.of.course.and.section$freq>1) 

```

#17,507 duplicates; possibly a non-traditional format for the class such as co-taught or field work with multiple supervisers; 
#Or some sort of coding error. Visual inspection of these sections indicates they are identical in grade distribution
#Since they are identical in grade distribution, we want to delete the duplicates to avoid overweighting the duplicates in our analysis below




=======================================================================================

=======================================================================================

=======================================================================================
## Question A (HEADING)

```{r}
# Click the green arrow on upper right corner to run the R code embedded
# within the enclosing 3 back-tick marks ```
date() # print out the current date
print("Hello world!")
var1 <- c(1:10)
for (i in var1) {
  print(i^2)
}
```

```{r}
# Break up large chunks of code for separate visible output
plot(cars)
```


### Answers to Question A

1. ANSWER 1 (This is an ordered or numbered list)
2. ANSWER _UNDERLINE_ OR *UNDERLINE*
3. ANSWER __BOLD__ **BOLD**

--------------------------------------------------------

## Question B

```{r}
# Code for Q.B - comment still works within code block
```

### Answers to Question B

- Part 1 (This is an unordered list)
- ITEM 2
    - Item 2.a
- Item 3

----------------------------------------------------------------------

## Question C

```{r}
# Code for Q.C
```

### Answers to Question C

1. answer 1
2. answer 2
3. answer 3

-------------------------------------------------------------------------

## Question D

```{r}
# Code for Q.d
```

### Answers to Question D

1. answer 1
2. answer 2
3. answer 3

----------------------------------------------------------------------

## Question E

```{r}
# Code for Q.E
```

### Answers to Question E

1. answer 1
2. answer 2
3. answer 3

-----------------------------------------------------------------------

## Question F

```{r}
# Code for Q.F
```

### Answers to Question F

1. answer 1
2. answer 2
3. answer 3

---------------------------------------------------------------------------

*END OF FILE* | 20190516 | Kristin Van Gaasbeck
