---
title: "Stat 128 Week 13 Class Lesson R Notebook"
output: html_notebook
author: "Dean Chiang"
---

# Homework Questions

```{r}
# h6 q1
probs1 <- dbinom(0:10, size = 10, p=0.5)
plot(0:10, probs1, type = "h")
```

## h6 q4

```{r}
factorial(3)
v1 <- 0:100
v2 <- 1/factorial(0:100)
head(v2)
head(cumsum(v2), 20)
```

## h6 q3
number of simulated values > 2/10000

prob sum is 7 when toss pair fair dice 
should be 1/6=.1666667

```{r}
mydicetosses = sample(1:6, 2000, replace=T)
mydicetoss.mat = matrix(mydicetosses, nrow=1000, ncol=2)
View(mydicetoss.mat)
sumofdice = apply(mydicetoss.mat, MARGIN = 1, sum)
results <- cbind(mydicetoss.mat, sumofdice)
View(results)
sum(sumofdice==7)
est.prob.seven = sum(sumofdice==7)/10000
est.prob.seven
```

## R Commands
```{r}
head(mtcars)
searchpaths()
head(mtcars$mpg)
attach(mtcars)
mpg
```

# Intro to Matrices in R

```{r}
mat1 <- matrix(1:9, nrow = 3, ncol = 3) # fill by columns
mat1
mat2 <- matrix(1:9, nrow = 3, byrow = T) # fill by row
mat2
mat3 <- matrix(NA, nrow = 3, ncol = 3)
mat3[1,1] <- 5
mat3
mat4 <- cbind(mat1, c(10, 11, 12))
mat4
```

## Matrix Arithmatic
```{r}
y <- matrix(c(2,4,3,1), nrow = 2)
y
x <- matrix(c(3,2,0,1), nrow = 2)
x
x+y
y*x
x/y
x^2
x^x
xy <- x %*% y
xy
transx <- t(x)
transx
detx <- det(x)
detx
# if a matrix is invertable then it can have an identity matrix
invx <- solve(x) # mult inverse of x, x^(-1)
invx
idmat <- diag(2)
idmat %*% x
x %*% solve(x)
```

### Extract Submatrix
```{r}
submat1 <- mat1[2:3, 2:3]
submat1
```

### Matrix Product
```{r}
apply(mat1, MARGIN = 2, prod)
```



# Intro to RSQLite

- [uwm data](https://www.kaggle.com/Madgrades/uw-madison-courses)
downlaoded to [folder](file:///Users/dean/Downloads/uw-madison-courses)
- [SQL tutorial](https://www.w3schools.com/sql/default.asp)
- [RSQLite ref](https://www.r-project.org/nosvn/pandoc/RSQLite.html)
- [RStudio SQLite](https://db.rstudio.com/databases/sqlite/)
- [RSQLite doc](https://www.rdocumentation.org/packages/RSQLite/versions/2.1.1)


## Download data and sql package
```{r}
# install.packages('RSQLite', dependencies = T) # DONE-20190429
# also installing the dependencies ‘bit’, ‘bit64’, ‘blob’, ‘DBItest’
library(RSQLite)
myconn = dbConnect(drv = SQLite(), ":memory")
str(myconn)
dbDisconnect(myconn)
```

## RSQLite 
```{r}
myconn2 <- dbConnect(drv = SQLite(), dbname = '/Users/dean/Downloads/uw-madison-courses/database.sqlite3')
str(myconn2)
```

### List tables
```{r}
dbListTables(myconn2)
```

### Query table
```{r}
dbListFields(myconn2, 'sections')
```

### Query table
```{r}
sections <- dbGetQuery(myconn2, "SELECT * FROM sections")
View(sections) # lots of NA
section.teach <- dbGetQuery(myconn2, "SELECT * FROM sections
                            INNER JOIN teachings
                            ON sections.uuid=teachings.section_uuid")
View(section.teach)
section.teach$instructor_id <- factor(section.teach$instructor_id)
library(plyr)
num.sections.by.instr <- count(section.teach, "instructor_id")
str(num.sections.by.instr$freq)
hist(num.sections.by.instr$freq)
```

## Exercise
```{r}
# Graph Year vs Number of Sections

```

